---
title: "DFM - End of Phase Surveys"
format: 
  html:
    toc: true
# format:
#   docx:
#     toc: true
#     number-sections: true
date: "`r format(Sys.time(), '%B %d %Y')`"
echo: false
warning: false
---

```{r libraries}
pacman::p_load(here,
               tidyverse, 
               gtsummary, 
               bstfun, 
               flextable,
               rstatix,
               openxlsx,
               Hmisc,
               magrittr,
               DT,
               car)

options(dplyr.summarise.inform = FALSE) 
```

```{r load_data, echo=FALSE, include=FALSE}
#source(str_c(here(), "/scripts/prepare_dataset.R"))
load(here("data", "eop_data.Rdata"))

# Remove un-necessary data frames
rm(eop_code_books, eop_files, eop1, eop2, eop4, q_labels, char_vec)

# Rename df codes to code_book and remove df_codes
code_book <- df_codes
rm(df_codes)

# We have grades for eop 3
# eop3 is class of 2022 (i.e. they graduated in 2022)
# Match data from 2022 are joined to eop3_grades

# Create a new data frame with a new variable that indicates whether or not a student matched into a primary care specialty
eop3_grades_match <- 
  left_join(eop3_grades,
          (match %>% filter(MatchYear == 2022)),
          by = "ResearchID") %>%
  #drop_na(Program_coded) %>%
  mutate(FM_Match = ifelse(grepl("Family Medicine", Program_coded), 1, 0)) %>%
  filter(ResearchID %in% eop3_grades$ResearchID)


# Rename variables
data <- 
  eop3_grades_match %>%
  rename("CPC_Eval" = EvalCC3_1,
         "CPC_Grade" = CRSE_GRADE_OFF,
         "Clerkship" = CRSE_LD,
         "Match" = Program_coded)

# Make a data frame of those that have a prelim residency
prelims <- 
  data %>% 
  filter(Match == "Prelim Year")

# For those that have a prelim, select the non-preliminary placement
data <- 
  bind_rows(
    (data %>% filter(!ResearchID %in% prelims$ResearchID)),
    (data %>% filter(ResearchID %in% prelims$ResearchID) %>% group_by(ResearchID) %>% slice_head())
  )


# For those that still have more than one placement, select the first
data <- 
  data %>%
  group_by(ResearchID) %>%
  slice_head() %>%
  ungroup()

# Check to count that data does not contain more than one placement
data %>%
  group_by(ResearchID) %>%
  count() %>%
  filter(n > 1) %>%
  nrow()

# Get the research IDs that do not have a match
missing_rids <- data %>% 
  filter(is.na(Match)) %>% 
  select(ResearchID)

# See if the missing research IDs are in the larger Match file
data %>%
  filter(ResearchID %in% missing_rids$ResearchID)

#write.csv(missing_rids, file = here("data", "IDs_w_out_a_match.csv"), row.names = FALSE)
# Per Wendy Christense at Office of assessment evaluation and outcomes: we do not have match 
# information for the missing research IDs. Almost all missing research IDs either graduated 
# in September 2022, instead of Spring 2022, or pushed back graduation to Spring 2023.
```

# Academic year 2020-2021
# 3rd-years, (Class Of 2022)

# Dataset
```{r display_data}
# cpc (community & primary care, )
data %>%
  select(CPC_Eval, CPC_Grade, Clerkship, LIC) %>%
  datatable(.)
```

# Demographics
## Matriculation age, gender, rural, and urm
```{r}
data %>%
  select(Matriculation_Age, Gender, Rural, URM, URM_AAMC) %>%
  tbl_summary()
```

## Race/Ethnicity
```{r}
data %>%
  select("Race/Ethnicity") %>%
  tbl_summary(sort = list(everything() ~ "frequency"))
```


## Track, LIC, Course grade
```{r}
data %>% 
  select(Track, LIC, CPC_Grade) %>%
  tbl_summary(sort = list(everything() ~ "frequency"))
```

# Data Summary
```{r display_summary}
data %>%
  select(CPC_Eval, CPC_Grade, ProfID, ProfID_1:ProfID_9) %>%
  summary(.) %>%
  knitr::kable(.)
```


```{r fig.cap="Poor (1), Fair (2), Good (3), Very Good (4), Excellent (5)"}
boxplot(eop3_grades$EvalCC3_1,
        main = "Primary Care Clerkship Evaluations",
        ylab = "Clerkship Quality Evaluation")
```

```{r, fig.cap="Grades are Withdraw (1), Pass (2), High Pass (3), Honors(4)"}
boxplot(eop3_grades$CRSE_GRADE_OFF,
        main = "Clerkship Grades",
        ylab = "Clerkship Grade")
```

```{r, fig.cap="Professional identification responses are Strongly disagree (1), Disagree (2), Neutral (3), Agree (4), Strongly agree (5)"}
profid <- eop3_grades %>%
  select(ProfID_1:ProfID) %>%
  pivot_longer(.,
               cols = c(ProfID_1:ProfID_9, ProfID),
               names_to = "Question", 
               values_to = "Score")

boxplot(Score ~ Question, data = profid,
        main = "Professional Identification Questionaire")    
```


# Research Question 1: 
What is the relationship between clerkship evaluations and grades from the family medicine and primary care clerkship?
```{r}
eop3_grades %>%
  filter(EvalCC3_1 != 9) %>%
  cor_test(
    EvalCC3_1, 
    CRSE_GRADE_OFF, 
    method = "kendall"
    ) %>%
  knitr::kable(.)

# Save the test statistic to a variable for reporting output
test_stat <- 
  eop3_grades %>%
  filter(EvalCC3_1 != 9) %>%
  cor_test(
    EvalCC3_1, 
    CRSE_GRADE_OFF, 
    method = "kendall"
    ) %>%
  pull(cor) 
```

There was a significant positive relationship between a student's clerkship evaluation and their grades from the family medicine and primary care clerkship, r<sub>$\tau$</sub> = `r test_stat[["tau"]]`, p (two-tailed) < 0.05.

# Research Question 2: 
What is the relationship between family medicine and primary care clerkship grades and professional identity in 3rd year medical students?
```{r}
eop3_grades %>%
  filter(EvalCC3_1 != 9) %>%
  cor_test(
    CRSE_GRADE_OFF, 
    ProfID, 
    method = "kendall"
    ) %>%
  knitr::kable(.)

# Save the test statistic to a variable for reporting output
test_stat <- 
  eop3_grades %>%
  filter(EvalCC3_1 != 9) %>%
  cor_test( 
    CRSE_GRADE_OFF,
    ProfID,
    method = "kendall"
    ) %>%
  pull(cor) 
```

Family medicine and primary care clerkship grades were not significantly related to a mean of professional identity scores, r<sub>$\tau$</sub> = `r test_stat[["tau"]]`, p (two-tailed) > 0.05.

# Research Question 3:
What is the relationship between a student’s match in primary care and factors such as rural upbringing, gender, matriculation age, LIC, and ProfID? Analyses exclude individuals who did not have data for the variable of interest.


## Match and Gender
```{r}
# What is the bivariate relationship between Match and Gender?
data %>%
  mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  select(Match, Gender) %>%
  tbl_summary(by = Match
              ) %>%
  add_p(everything()~"chisq.test")


# Chi square test, all match categories
#chisq.test(table(data$Match, data$Gender))

# Chi square test, binary FM match category
# chisq.test(table(data %>%
#   mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
#   select(Match, Gender) %>% pull(Match), data$Gender))
```


## Match and Matriculation Age
```{r}
# What is the bivariate relationship between Match and Age?
data %>%
  mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM"),
         Age = as.numeric(Matriculation_Age)) %>%
  select(Match, Age) %>%
  tbl_summary(by = Match,
              statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  add_p(everything() ~ "t.test")
```


## Match and URM
### URM
```{r}
data %>%
  mutate(URM = factor(as.character(na_if(URM, "Unknown"))),
         Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  drop_na(URM) %>%
  select(Match, URM) %>%
  tbl_summary(by = Match
              ) %>%
  add_p(everything()~"chisq.test")
```

### URM_AAMC
```{r}
data %>%
  mutate(URM_AAMC = factor(as.character(na_if(URM_AAMC, "Unknown"))),
         Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  drop_na(URM_AAMC) %>%
  select(Match, URM_AAMC) %>%
  tbl_summary(by = Match,
              missing = "no",
              ) %>%
  add_p(everything()~"chisq.test")
```


## Match and LIC
```{r}
# LIC
data %>%
  mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  select(Match, LIC) %>%
  tbl_summary(by = Match,
              missing = "no",
              ) %>%
  add_p(everything()~"chisq.test")
```

## Match and Rural
```{r}
# Rural
data %>%
  mutate(Rural = factor(as.character(na_if(Rural, "Unknown"))),
         Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  select(Match, Rural) %>%
  tbl_summary(by = Match,
              missing = "no",
              ) %>%
  add_p(everything()~"chisq.test")
```

## Match and Community & Primary Care Clerkship Grades
```{r}
# CPC Grades
data %>%
  mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  select(Match, CPC_Grade) %>%
  tbl_summary(by = Match,
              missing = "no",
              type = list(CPC_Grade ~ "continuous", Match ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  #add_p(everything()~"chisq.test")
  add_p(everything()~"t.test")

```

## Match and Community & Primary Care Clerkship Evals
```{r}
# CPC Evals
data %>%
  mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  select(Match, CPC_Eval) %>%
  tbl_summary(by = Match,
              missing = "no",
              type = list(CPC_Eval ~ "continuous", Match ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  add_p(everything()~"t.test")

```


## Match and Professional Identification Composite
```{r}
# # Professional ID composite
# data %>%
#   mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
#   select(Match, ProfID) %>%
#   tbl_summary(by = Match,
#               missing = "no",
#               ) %>%
#   add_p(everything()~"chisq.test")



# ProfID as a continuous variable
data %>%
  mutate(Match = ifelse(Match == "Family Medicine", "FM", "Non-FM")) %>%
  select(Match, ProfID) %>%
  tbl_summary(by = Match,
              missing = "no",
              type = list(ProfID ~ "continuous", Match ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  add_p(everything()~"t.test")

```